Reproducible Summary Tables with the \pkg{gtsummary} Package

### 2021-04-13 gtsummary_submission.tex
overleaf

% \newpage
\begin{example}
trial %>%
  select(marker, response, trt) %>%
  tbl_summary(by = trt, missing = "no",
              statistic = list(marker ~ "{mean} ({sd})")) %>%
  add_difference() %>%
  add_n() %>%
  add_stat_label() %>%
  bold_labels() %>%
  modify_header(list(label ~ "**Variable**", all_stat_cols() ~ "**{level}**")) %>%
  modify_spanning_header(all_stat_cols() ~ "**Randomization Assignment**") %>%
  as_gt() %>%
  gt::tab_header(
    title = gt::md("**Table 1. Treatment Differences**"),
    subtitle = gt::md("_Highly Confidential_")
  ) %>%
  gt::tab_source_note("Data updated June 26, 2015")
\end{example}
\begin{widefigure}[h!]
  \includegraphics[scale=0.49]{custom.png}
  \centering
\end{widefigure}

>>>>

% \newpage
\begin{example}
trial %>%
  select(marker, response, trt) %>%
  tbl_summary(by = trt, 
              missing = "no",
              statistic = marker ~ "{mean} ({sd})") %>%
  add_difference() %>%
  add_n() %>%
  add_stat_label() %>%
  bold_labels() %>%
  modify_header(list(label ~ "**Variable**", all_stat_cols() ~ "**{level}**")) %>%
  modify_spanning_header(all_stat_cols() ~ "**Randomization Assignment**") %>%
  as_gt() %>%
  gt::tab_header(
    title = gt::md("**Table 1. Treatment Differences**"),
    subtitle = gt::md("_Highly Confidential_")
  ) %>%
  gt::tab_source_note("Data updated June 26, 2015")
\end{example}
\begin{widefigure}[h!]
  \includegraphics[scale=0.49]{custom.png}
  \centering
\end{widefigure}
